Wildcard: a tool for modifying websites by directly manipulating data tables

### 2019-12-28 paper.tex
rework deployment for my website

@@

\title{Wildcard: a tool for modifying websites without programming}
\subtitle{}% optional

@@

@@

There have been many research projects that try to address these
hurdles. For example, Chickenfoot allows for people to more quickly
modify sites without using Javascript or dealing with the DOM, directly
addressing both of these barriers. But, a decade later, not many people
have ended up using systems like this.

@@

\hypertarget{the-wildcard-platform}{%
\subsection{The Wildcard platform}\label{the-wildcard-platform}}

@@

@@

@@

@@

\hypertarget{example-use-cases}{%
\section{Example use cases}\label{example-use-cases}}

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\title{Wildcard: a tool for modifying websites by directly manipulating
data tables}
\subtitle{}% optional

@@

Todos in intro:

\begin{itemize}
\tightlist
\item
  hook with Airbnb sort
\item
  add more reasons
\item
  make this shorter
\end{itemize}

@@

There have been many research projects that try to address these
hurdles. For example, Chickenfoot \autocite{miller2010} allows for
people to more quickly modify sites without using Javascript or dealing
with the DOM, directly addressing both of these barriers. But, a decade
later, not many people have ended up using systems like this.

\hypertarget{why-dont-people-tweak-websites}{%
\subsubsection{Why don't people tweak
websites?}\label{why-dont-people-tweak-websites}}

@@

\hypertarget{the-wildcard-platform}{%
\subsubsection{The Wildcard platform}\label{the-wildcard-platform}}

@@

For example, here we open up a table view that corresponds to search
results on the Airbnb travel site.

Todos here:

\begin{itemize}
\tightlist
\item
  a better demo is actually sorting too at this point too, to show the
  bidirectional nature
\item
  hint at future possibilities
\item
  introduce an image fallback for the PDF version
\end{itemize}

@@

\hypertarget{directness}{%
\subsubsection{Directness}\label{directness}}

@@

\hypertarget{the-big-picture}{%
\subsubsection{The big picture}\label{the-big-picture}}

@@

\hypertarget{demo}{%
\section{Demo}\label{demo}}

\begin{itemize}
\tightlist
\item
  Sorting search results:

  \begin{itemize}
  \tightlist
  \item
    Airbnb took away search
  \item
    once you see the tabular view, there's an obvious interaction
    available to anyone familiar with tables
  \end{itemize}
\item
  Injecting new data into the page

  \begin{itemize}
  \tightlist
  \item
    Take own custom notes, saved in the browser. Maybe shared in the
    future
  \end{itemize}
\item
  Formulas

  \begin{itemize}
  \tightlist
  \item
    Compute values to inject into the page
  \item
    TBD: styling
  \end{itemize}
\item
  Using a custom date picker
\end{itemize}

\hypertarget{design-principles}{%
\section{Design principles}\label{design-principles}}

\hypertarget{expose-generic-structure}{%
\subsection{Expose generic structure}\label{expose-generic-structure}}

\begin{itemize}
\tightlist
\item
  Consistent across all sites, can gain familiarity
\item
  Nightmare bike: users learn the structure they can exploit
\end{itemize}

\hypertarget{no-api-needed}{%
\subsection{No API needed}\label{no-api-needed}}

\begin{itemize}
\tightlist
\item
  3p-only is enough. 1p help is optional.
\item
  Can even do things the 1p didn't want to expose.
\end{itemize}

\hypertarget{in-place-toolchain}{%
\subsection{In-place toolchain}\label{in-place-toolchain}}

\begin{itemize}
\tightlist
\item
  meet the user where they are, in the page
\item
  very native to the web style (dev tools is kinda like this)
\end{itemize}

\hypertarget{decouple-ui-from-data}{%
\subsection{Decouple UI from data}\label{decouple-ui-from-data}}

\begin{itemize}
\tightlist
\item
  bring your own views of the data
\item
  bring your own widgets for data entry
\item
  instrumental interaction
\end{itemize}

\hypertarget{analysis}{%
\section{Analysis}\label{analysis}}

Cognitive dimensions?

\hypertarget{related-work}{%
\section{Related work}\label{related-work}}

\begin{itemize}
\tightlist
\item
  Instrumental interaction
\item
  Web automation
\item
  Wrapper induction
\item
  Personal data
\item
  Extension helpers
\end{itemize}

\hypertarget{future-work-open-questions}{%
\section{Future work / Open
Questions}\label{future-work-open-questions}}

\begin{itemize}
\tightlist
\item
  How far does functionality go?

  \begin{itemize}
  \tightlist
  \item
    workflows? triggers?
  \item
    what can and can't be done?

    \begin{itemize}
    \tightlist
    \item
    \end{itemize}
  \end{itemize}
\item
  automated wrappers?

  \begin{itemize}
  \tightlist
  \item
    lean on existing tech
  \end{itemize}
\item
  usability studies
\end{itemize}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

\hypertarget{todos}{%
\section{Todos}\label{todos}}

\begin{itemize}
\tightlist
\item
  remove bold text for the proceedings version
\end{itemize}
